Trends of SDR in Thessaloniki

### 2023-06-12 Article.Rmd
Commit 2023-06-12 10:17
Commit 2023-06-12 12:17

```{r echo=F, include=T}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = '!ht'   )
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

<!-- aggregation -->
Before further analysis and deseasonalization, we implement an appropriate aggregation scheme on the 1-minute data. To preserve the representativeness we use the following criteria:
a) for daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values were indexed based on the day of year number, and the monthly by the corresponding calendar month.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
Thus, for each data set we have obtained the relative departure of the seasonal mean.
These values are presented in the following section.

........

................

## SZA Aggregation

Both datasets were aggregate in $1^\circ$ SZA bins by am, pm, am+pm

by daily mean

daily sum

seasonal daily mean

filtering of means

statistical significance

Significance and aggregation scheme and filtering will be noted along with the corresponding results.

@@

```{r szatrends, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/SzaTrends-5.pdf", "./images/SzaTrends-21.pdf"))
```

>>>>

```{r echo=F, include=T}
## document configurations 
knitr::opts_chunk$set(comment    = ""      )
knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
library(pander)
library(data.table)
## load data
load("./data/common_data_14_2.Rda")
TSIinfo <- data.table(read.csv("./figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
## variables we use
source("~/MANUSCRIPTS/2022_sdr_trends/DHI_GHI_0_variables.R")
```

@@

<!-- aggregation -->
Before further analysis and deseasonalization, we implement an appropriate aggregation scheme on the 1-minute data. To preserve the representativeness we use the following criteria:
a) for daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values were indexed based on the day of year number, and the monthly by the corresponding calendar month.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by season (December - February: Winter, March - May: Spring, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
<!-- SZA Deseasonalization -->
In addition to the previous aggregation scheme, each dataset was aggregate in $1^\circ$ SZA bins, separate for cases before and after local noon. 
This gave us an approximation of Sun's SZA contribution to the SDR brightening.

Thus, for each data set we have obtained the relative departure of the seasonal mean.
The statistical significance and aggregation scheme and filtering will be noted along with the corresponding results.

@@

```{r szatrends, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.35\\linewidth', fig.asp=1, fig.ncol = 2}
knitr::include_graphics(c("./images/SzaTrends-13.pdf", "./images/SzaTrends-21.pdf"))
```
